Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-07 doc/report/discussion.tex
adding files to the report
added some texts to the report, and a glass FSM figure
finished implementation, and start discussion

\section{Design}
\label{sec:design}

Talks about the system design space.
What might be available to achieve such a function.

>>>>

\section{Discussion}
\label{sec:discussion}

\textcolor{red}{Discuss the problems we have encountered and other random stuffs in this section.}

\subsection{Interaction in Attention}
\label{sec:inter-attent}

During our brainstorming and discussion of this idea, we have identified some tasks where user might not pay their attention to the device they are controlling. One such example is giving presentation. The attention of presenter is to interact with the audience, but this is achieved through controlling the slides and projection.

### 2013-05-07 doc/report/implementation.tex
finished implementation, and start discussion

\subsection{Clients}
The clients are comprised of a main Arduino board, an IR receiver, an XBee radio, and various actuators. We used Arduino Uno, which has an ATmega328 microcontroller and suffice our purpose in this project. We use off-the-shell IR receivers ({\color{red} confirm it is PNA4602}), which outputs 0V (low) on detection of 38 KHz carrier or 5V (high) otherwise. The XBee radio, accompanied with an XBee modems, takes charge of the communication with the Glass. Additional components are subject to the device being attached to. In our current system, we have a relay ({\color{red} need to know relay model}) which can control the AC power plug, and we have a USB connected computer to control video playing.

@@

{\color{red} I arrived here for the second pass - Ben}

@@

The Glass is complicated in two folds. First, we move the complexity of coordinating all clients to the Glass. Second, we have to handle user gesture on Glass. For a clean design, we separate the gesture detection and XBee transmission into two customized library, and only expose interesting information to the main program.

The whole work flow is as follows. When the user hasn't shown any interest of interaction, the system lives in {\it IDLE} state. When ``tap'' is detected, the Glass will broadcast IR signal to inform the devices which is in front of the user (the one that can receive IR signal). Then the Glass waits for a specific period of time for acknowledge message sent by clients. The timer in {\it WAIT} state now is set to 1 second. When timer expires, Glass will go to {\it IDLE} if no client has responded, or {\it CONFIRM} if it receives just one message. However, the complicated case is when there are multiple clients that have received IR signal and responded. Though we expect such scenario is rare, there is still chance that the physical devices are put together and it is necessary to differentiate them. In this case, the system goes to {\it VERIFY} state, and send out corresponding verifying message based on user's gesture. Once the user confirmed the selection, it goes to {\it CONNECTED} state where it's ready to send out commands. Again, to illustrate the flows, we have the FSM in Fig.\,\ref{fig:glassFSM}.

@@

The gateway provides access to the personal area network for computers, and presumably this can be further open to the Internet. Since there have already been many products \cite{NinjaBlocks, Lockitron} that essentially function in this way, we do not spend much time on this aspect in our project.

Just for completeness, we wrote a python script that controls a USB XBee adaptor, so that we can remotely control those devices without the Glass and IR initiation.

>>>>

\subsection{Clients}
The clients are comprised of a main Arduino board, an IR receiver, an XBee radio, and various actuators. We used Arduino Uno, which has an ATmega328 microcontroller and suffice our purpose in this project. We use off-the-shell IR receivers ({\color{red} confirm it is PNA4602}), which outputs 0V (low) on detection of 38 KHz carrier or 5V (high) otherwise. The XBee radio, accompanied with an XBee modems, takes charge of the communication with the Glass. LEDs are added as an indicator of the state of clients and visual feedback for users. Additional components are subject to the device being attached to. In our current system, we have a relay ({\color{red} need to know relay model}) which can control the AC power plug, and we have a USB connected computer to control video playing. The prototype is shown in Fig.\,\ref{fig:client}.

{\color{red} add clients photos here}
\begin{figure}
  \centering
%  \includegraphics[width=\linewidth]{../figs/client.png}
  \caption{Prototype of the clients}
  \label{fig:client}
\end{figure}

@@

@@

The Glass is complicated in two folds. First, we move the complexity of coordinating all clients to the Glass. Second, we have to handle user gesture on Glass. From an engineer perspective, we separate the gesture detection and XBee transmission into two customized library files in Arduino. And only interesting information is exposed to the main program. We use the same Arduino Uno and XBee module as the client. In addition, we have a membrane potentiometer (100 mm long) as the slider to take user's input, and the most important IR emitter to broadcast IR signals. After we've put the components onto the Glass, we have the prototype shown in Fig.\,\ref{fig:glass}.

{\color{red} add glass photos here}
\begin{figure}
  \centering
%  \includegraphics[width=\linewidth]{../figs/glass.png}
  \caption{Prototype of the Glass}
  \label{fig:glass}
\end{figure}

The whole work flow on the Glass is as follows. When the user hasn't shown any interest for interaction, the system stays in {\it IDLE} state. When ``tapping'' is detected, the Glass will broadcast IR signals to inform the devices which are in front of the user. Since we have the tube around the IR transmitter, the resulting signal coverage is a pretty straight line. After the Glass has sent out IR message, at this time, it doesn't know how many devices might respond. In this case, the Glass would wait for a specific period of time, and count the number of acknowledgement messages sent by clients. To ensure responsiveness to end user, we set the timer in {\it WAIT} state to be 1 second. When the timer expires, Glass will go to {\it IDLE} if no client has responded, or {\it CONFIRM} if it receives just one message. However, the complicated case is when there are multiple clients that have received the IR signal (because they are near to each other) and responded. Though we expect this scenario rarely happens, there is still chance when the physical devices are put together and it is necessary to differentiate them. In this case, the system goes to {\it VERIFY} state, and sends out corresponding verifying message based on user's gesture. We adopt the slider on glass to change active selection. Once the user confirmed the selection, it goes to {\it CONNECTED} state and now the Glass is ready to send out commands. We have the FSM in Fig.\,\ref{fig:glassFSM}.

We've configured the XBee modules such that the Glass can talk in both direction with all clients, while clients cannot talk with each other. In this way, the Glass would serve as master of this personal area network (PAN), whose ID is 4321 in our scenario.

@@

The gateway provides access to this PAN for computers, and presumably this can be further open to the Internet. Since there have already been many products \cite{NinjaBlocks, Lockitron} that essentially function in this way, we do not spend much time on this aspect in our project.

For completeness, we wrote a python script that controls a USB XBee adaptor. And this XBee module has the same configuration as the Glass, so it serves as the master of the network. This enables the remote control of the clients.
